---
title: "Getting Tweeters"
subtitle: "Oxford Spring School, 2022"
author: Christopher Barrie
format: revealjs
editor: visual
---

## Introduction

-   Why get tweet*ers*?
    -   Get network characteristics
    -   Get user demographics
    -   Linked survey designs

## Introduction

-   Before that: getting data outside the API
    -   Datasets shared online, e.g.,:

        -   [Harvard Dataverse](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/2FIFLH)

        -   <https://catalog.docnow.io/>

        -   [Zenodo](https://zenodo.org/record/4540820#.YmJTYcaEaLc)
        
## Hydrating

```{r, eval = T, echo = T}
tweet_IDs <- readRDS("data/wm_IDs_samp.rds")
head(tweet_IDs)
```

```{r, eval = F, echo = T}
library(academictwitteR)

hydrated_tweets <- hydrate_tweets(tweet_IDs)
```

## Hydrating

Alternatively:

Use the [hydrator](https://github.com/DocNow/hydrator#readme) tool from DocTheNow

## Getting tweeters

```{r, eval = T, echo = T}
library(academictwitteR)
library(dplyr)
library(lubridate)
library(ggplot2)


cjb_ID <- get_user_id("cbarrie")
cjb_ID

```

## Getting whom I follow (friends)

::: panel-tabset
### IDs

```{r, eval = F, echo = T}
userfwing <- get_user_following(cjb_ID)

ids <- userfwing$id

head(ids)
```

```{r, eval = T, echo = F}
userfwing <- readRDS("data/cjbfwing.rds")
ids <- userfwing$id
head(ids)
```

### User data

```{r, eval = T, echo = F}
userfwingsamp <- userfwing %>%
  sample_n(20)
kableExtra::kable(userfwingsamp)
```
:::

## User-level inference

Example from [here](https://github.com/euagendas/m3inference)

```{python, eval = F, echo = T}

from m3inference import M3Inference
import pprint
m3 = M3Inference() # see docstring for details
pred = m3.infer('./test/data_resized.jsonl') # also see docstring for details
pprint.pprint(pred)
```

    OrderedDict([('720389270335135745',
                  {'age': {'19-29': 0.1546,
                           '30-39': 0.114,
                           '<=18': 0.0481,
                           '>=40': 0.6833},
                   'gender': {'female': 0.0066, 'male': 0.9934},
                   'org': {'is-org': 0.7508, 'non-org': 0.2492}}),
                 ('21447363',
                  {'age': {'19-29': 0.0157,
                           '30-39': 0.9837,
                           '<=18': 0.0004,
                           '>=40': 0.0002},
                   'gender': {'female': 0.9866, 'male': 0.0134},
                   'org': {'is-org': 0.0002, 'non-org': 0.9998}}),
        ...
      ...

## User-level inference

```{r, eval = T, echo = T}
devtools::install_github("pablobarbera/twitter_ideology/pkg/tweetscores")
library(tweetscores)
```

## User-level inference

```{r, eval=F, echo = T}
results <- estimateIdeology("cbarrie", ids)
plot(results)
```

```{r, eval=T, echo = F}
results <- readRDS("data/cjbtscore.rds")
plot(results)

```

## User-level geolocation

```{r, eval = T, echo = T}
userfwing %>%
  group_by(location) %>%
  summarise(count = n()) %>%
  top_n(count)
```
